Exploratory Analysis Script

### 2024-04-05 code/eda-code/eda.qmd
Updated manuscript to reflect the updates for the pred.table

# Create table 
selected_variables %>%
  tbl_summary(
    by = region,
    label = list(wra ~ "Number of women of reproductive age, 15-49"),
    type = all_continuous() ~ "continuous2",
    statistic = list(all_continuous() ~ c("{mean}","{min}, {max}"))) %>%
modify_header(label ~ "**Predictor Variable**") %>%
modify_caption("**Table 1. Predictor Variables**") %>%
modify_spanning_header(all_stat_cols() ~ "Region")

>>>>

# Create table 
predictortable <-selected_variables %>%
  tbl_summary(
    by = region,
    label = list(wra ~ "Number of women of reproductive age, 15-49"),
    type = all_continuous() ~ "continuous2",
    statistic = list(all_continuous() ~ c("{mean}","{min}, {max}"))) %>%
modify_header(label ~ "**Predictor Variable**") %>%
modify_caption("**Table 1. Predictor Variables**") %>%
modify_spanning_header(all_stat_cols() ~ "Region")
